### 2016-05-24 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Adding dimensions to pic of BDPs in hose stream report; minor edits to gas burner report
Minor edits to gas burner report, new annotation on BDP pic

\begin{figure}[!ht]
	\includegraphics[width=0.45\columnwidth]{../Figures/Pictures/doorway_BDPs}
	\\~\\
	\includegraphics[width=0.65\columnwidth]{../Figures/Pictures/roof_vent_BDPs.png}
	\caption[Bi-directional probe plus solid thermocouple arrays in East Structure.]{Bi-directional probe plus solid thermocouple array in exterior doorway (top) and in roof vent (bottom) of the East Structure.}
	\label{fig:BDP_arrays}
\end{figure}

@@

\subsubsection{Gas Flow Meter}

@@

\begin{table}[!ht]
\caption{Calculated Heat Release Rate for East Structure Tests}
\begin{tabular}{lccccc}
 \toprule
 					& 	\multicolumn{5}{c}{\textbf{Heat Release Rate (kW)}} \\
\textbf{Test} 		&	\begin{tabular}{c} Corner \\ Burner On \end{tabular} 
					&	\begin{tabular}{c} Middle \\ Burner On \end{tabular}
					&	\begin{tabular}{c} Center \\ Burner On \end{tabular}
					& 	\begin{tabular}{c} Center \\ Burner Off \end{tabular}
					&   \begin{tabular}{c} Middle \\ Burner Off \end{tabular} \\
 \midrule
Test 2 				& 338 & 651	& 894 & 634 & 330 \\
Test 3				& 326 & 650	& 899 & 631 & 326 \\
Test 4				& 351 & 654	& 902 & 652 & 337 \\
Test 5 - Seq. 1		& 263 & 526	& 723 & 486 & 263 \\
Test 5 - Seq. 2		& 225 & 526	& 727 & 526 & 316 \\
Test 5 - Seq. 3		& 263 & 526	& 722 & 526 & 263 \\
Test 6 - Seq. 1		& 263 & 526	& 722 & 526 & 263 \\
Test 6 - Seq. 2		& 225 & 526	& 718 & 526 & 287 \\
Test 6 - Seq. 3		& 263 & 526	& 714 & N/A & N/A \\
\bottomrule
\end{tabular}
\label{table:HRR_East}
\end{table}

@@

\begin{table}[!ht]
\caption{Calculated Heat Release Rate for West Structure Tests}
% \begin{tabular}{lc}
%  \toprule
% \textbf{Test}  			& 	\begin{tabular}{c} \textbf{Heat Release Rate} \\ \textbf{(kW)} \end{tabular} \\
% \midrule
% Test 22 				& 	756		\\
% Test 23					& 	788		\\
% Test 24					& 	784		\\
% Test 25					&  	785		\\
\begin{tabular}{lccc}
 \toprule
 					& 	\multicolumn{3}{c}{\textbf{Heat Release Rate (kW)}} \\
\textbf{Test} 		& 	1 Burner On 	& 	2 Burners On 	& 	3 Burners On \\
 \midrule
Test 22				& 	  287		 	&      316			&     	759 	  \\
Test 23				& 	  395		 	&      526			&     	788 	  \\
Test 24				& 	  287		 	&      631			&     	787 	  \\
Test 25				& 	  N/A		 	&      N/A			&     	785 	  \\
\bottomrule
\end{tabular}
\label{table:HRR_West}
\end{table}

@@

% \begin{landscape}
% \begin{table}[!ht]
% \caption{East Structure experimental event times (mm:ss)}
% \begin{tabular}{lcccccccccccccc}
%  \toprule
% \textbf{Test} &
% \multicolumn{2}{c}{\textbf{\underline{Corner Burner}}} &
% \multicolumn{2}{c}{\textbf{\underline{Middle Burner}}} &
% \multicolumn{2}{c}{\textbf{\underline{Center Burner}}} &
% \multicolumn{2}{c}{\textbf{\underline{W Double Door}}} &
% \multicolumn{2}{c}{\textbf{\underline{E Double Door}}} &
% \multicolumn{2}{c}{\textbf{\underline{Single Door}}} &
% \multicolumn{2}{c}{\textbf{\underline{Roof Vent}}}
% \\
% \textbf{Number} &
% \textbf{On} & \textbf{Off} & \textbf{On} & \textbf{Off} & \textbf{On} & \textbf{Off} &
% \textbf{Close} & \textbf{Open} & \textbf{Close} & \textbf{Open} &
% \textbf{Close} & \textbf{Open} & \textbf{Close} & \textbf{Open}
% \\
% \midrule
% % Test 2
% 2 & 0:20 & 16:20 & 3:20 & 14:20 & 6:20 & 12:20 &
% N/A & 7:20 & N/A & 9:20 & N/A & 10:30 & N/A & N/A \\
% % Test 3
% 3 & 0:20 & 17:20 & 3:20 & 15:20 & 6:20 & 13:20 &
% N/A & 7:20 & N/A & 9:20 & N/A & 10:20 & N/A & N/A \\
% % Test 4
% 4 & 0:20 & 17:20 & 3:20 & 15:20 & 6:20 & 13:20 &
% N/A & 7:20 & N/A & 9:20 & N/A & 10:20 & N/A & N/A
% \\ \multicolumn{15}{c}{ } \\
% % Test 5a
% 5a & 0:15 & 9:55 & 0:30 & 9:35 & 0:45 & 9:15 &
% N/A & 3:18 & N/A & 6:18 & N/A & N/A & 7:45 & 2:53 \\
% % Test 5b
% 5b & 0:15 & 10:30 & 0:30 & 10:15 & 0:45 & 10:00 &
% N/A & 3:45 & N/A & 5:15 & N/A & N/A & 8:30 & 2:15 \\
% % Test 5c
% 5c & 0:15 & 9:45 & 0:30 & 9:30 & 0:45 & 9:15 &
% N/A & 3:45 & N/A & 5:16 & N/A & N/A & 7:28 & 2:15
% \\ \multicolumn{15}{c}{ } \\
% % Test 6a
% 6a & 0:15 & 9:55 & 0:30 & 9:35 & 0:45 & 9:15 &
% N/A & 3:18 & N/A & N/A & N/A & N/A & N/A & 2:53 \\
% % Test 6b
% 6b & 0:15 & 9:55 & 0:30 & 9:35 & 0:45 & 9:15 &
% N/A & 3:18 & N/A & N/A & N/A & N/A & N/A & 2:53 \\
% % Test 6c
% 6c & 0:15 & 9:55 & 0:30 & 9:35 & 0:45 & 9:15 &
% N/A & 3:18 & N/A & N/A & N/A & N/A & N/A & 2:53 \\
% \bottomrule
% \end{tabular}
% \label{table:east_exp_times}
% \end{table}
% \end{landscape}

>>>>

\begin{figure}[!ht]
	\includegraphics[width=0.45\columnwidth]{../Figures/Pictures/doorway_BDPs}
	\\~\\
	\includegraphics[width=0.65\columnwidth]{../Figures/Pictures/roof_vent_BDPs.png}
	\caption[Bi-directional probe plus solid thermocouple arrays in East Structure.]{Bi-directional probe plus solid thermocouple array in south exterior doorway (top) and in roof vent (bottom) of the East Structure.}
	\label{fig:BDP_arrays}
\end{figure}

@@

\subsubsection{Gas Flow Meter}
A rotary type gas meter was used to measure the flow of propane to the gas burners. The manufacturer of the meter quantifies the maximum error as 2\%.

% http://www.istec-corp.com/products/gas-meter-model-romet-rm-series-rotary.pdf

@@

\begin{table}[!ht]
\caption{Calculated Heat Release Rate for East Structure Tests}
\begin{tabular}{lccccc}
 \toprule
 					& 	\multicolumn{5}{c}{\textbf{Heat Release Rate (kW)}} \\
\textbf{Test} 		&	\begin{tabular}{c} Corner \\ Burner On \end{tabular} 
					&	\begin{tabular}{c} Middle \\ Burner On \end{tabular}
					&	\begin{tabular}{c} Center \\ Burner On \end{tabular}
					& 	\begin{tabular}{c} Center \\ Burner Off \end{tabular}
					&   \begin{tabular}{c} Middle \\ Burner Off \end{tabular} \\
 \midrule
Test 2$^*$ 			& 338 & 651	& 901 & 634 & 330 \\
Test 3$^*$			& 326 & 650	& 905 & 631 & 326 \\
Test 4				& 351 & 654	& 952 & 652 & 337 \\
Test 5 - Seq. 1		& N/A & N/A	& 725 & N/A & N/A \\
Test 5 - Seq. 2		& N/A & N/A	& 728 & N/A & N/A \\
Test 5 - Seq. 3		& N/A & N/A	& 723 & N/A & N/A \\
Test 6 - Seq. 1		& N/A & N/A	& 722 & N/A & N/A \\
Test 6 - Seq. 2		& N/A & N/A	& 721 & N/A & N/A \\
Test 6 - Seq. 3		& N/A & N/A	& 714 & N/A & N/A \\
\bottomrule
\end{tabular}
\label{table:HRR_East}
\end{table}

@@

\begin{table}[!ht]
\caption{Calculated Heat Release Rate for West Structure Tests}
\begin{tabular}{lc}
 \toprule
\textbf{Test} 		& 	\textbf{Heat Release Rate (kW)}	\\
 \midrule
Test 22				&     	764 	  \\
Test 23				&     	789 	  \\
Test 24				& 	    789 	  \\
Test 25				&     	786 	  \\
\bottomrule
\end{tabular}
\label{table:HRR_West}
\end{table}

@@
